### 2018-10-09 paper/finitecomplete-failures.tex
removed fixmes following our meeting
Extended proof for Lemma 6

\paragraph{Step~2.} Since $Q\ conf\ P$, Lemma~\ref{lemma:hseta} implies
that for all $s\in\trc(Q)\cap\trc(P)$, every $H \in \minhits(P/s)$ is a
hitting set for $\minaccs(Q/s)$. From Lemma~\ref{lemma:ufproperties} we know
that $U_F(j)/s = U_F(j,k,n)$ with $U_F(j,k,n) = U_F(j,\#s,G(P)/s)$, so
$\minhits(n) = \minhits(P/s)$. The branch (\ref{eq:ufb}) of the test
$U_F(j,k,n)$ leads always to a PASS verdict and is taken if $\minhits(n) =
\varnothing$. The branch (\ref{eq:ufc}) always leads to test continuation
without a verdict. Since, $s$ is a trace of $P$ and $Q$, we know that there
is a behaviour of $Q$ that will accept an event $e$ in that branch and allow
the test to proceed. \fixme{I think we need a stronger argument here, as to
why it cannot deadlock.} \fxnote{jp: I do not understand the question --
let's discuss this on the phone. See what I wrote. I'm still worried because
of nondeterminism. } For the last branch, we note that it can only be entered
if $\minhits(P/s) = \minhits(n) \neq\varnothing$. In this case, any selected
minimal hitting set $H\in\minhits(n)$ has a non-empty intersection with each
of the minimal acceptances of $Q/s$. As a consequence, $Q/s$ never blocks
when offered events from $H\in\minhits(n)$, and the test terminates with
event $\epass$. Note that this argument requires that $Q$ is free of
livelocks, because otherwise the $\epass$-events might not become visible,
due to unbounded sequences of hidden events performed by $Q$. \xbox
\end{proof}
%
\begin{lemma}\label{lemma:mainfexhaustive}
A test suite $\TS_F$ specified as in Theorem~\ref{th:failurestest} is
exhaustive for the fault model specified there.
\end{lemma}
\begin{proof}
Consider a process $Q\in{\cal D}$ with $P\not\lessdet_F Q$. According to
(\ref{eq:failconf}), this non-conformance can be caused in two possible ways
corresponding to the cases $P\not\lessdet_T Q$ and $\neg(Q\ conf\ P)$. These
cases can be characterised as follows:
\begin{description}
\item[Case~1] $\trc(Q)\not\subseteq \trc(P)$
\item[Case~2] There exists a joint trace $s\in\trc(Q)\cap\trc(P)$ and a minimal acceptance $A_Q$
of $\minaccs(Q/s)$, such that
(see Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb})).
\begin{equation}
\label{eq:accsnotcontained}
\forall A_P\in\minaccs(P/s): A_P\not\subseteq A_Q,
\end{equation}
\end{description}
It has to be shown for each of these cases that at least one test execution
of some $(Q\parallel[\Sigma] U_F(j))$ with $j < pq$ ends with the $\efail$
event or deadlocks. We do this by analysing the product graph of the
reference process $P$ and the SUT process $Q$: any trace
$s\in\trc(Q)\cap\trc(P)$ gives rise to a path labelled by the events of $s$
through this product graph. Any error can be detected after running through
such a trace and then either observing an event outside $[P/s]^0$ (this is
the violation described by Case~1) or identifying an illegal acceptance $A_Q$
as specified in Case~2. It is not guaranteed, however, that trace $s$ is
short enough to be executed by one of the test cases $U_F(j)$ with $0\le j <
pq$. So, it has to be shown that for any $s$ leading to an error situation
specified by Case~1 or Case~2, there exists a trace $u$ of maximal length
$pq-1$ leading to the same error.

>>>>

\paragraph{Step~2.} For proving that a test execution can never deadlock without a 
$\epass$ event, it has to be shown that a test execution can neither block
at branch (\ref{eq:ufc}) nor at branch (\ref{eq:ufd}).

\paragraph{Step~2.1} Suppose that the test execution blocks at branch (\ref{eq:ufc})
after having run through trace $s$ with $\#s < j$. 
Since  $P\lessdet_T Q$ by assumption, $s$ is a trace of $P$, thus 
$U_F(j)/s = U_F(j,\#s,G(P)/s)$ according to Lemma~\ref{lemma:ufproperties}. Therefore,
$U_F(j)/s$  can enter  branch (\ref{eq:ufc}) with any event from $[G(P)/s]^0$.
Since we assume that $(Q\parallel[\Sigma] U_F(j))/s$ deadlocks, this means that
$[G(P)/s]^0$ is {\it not} a hitting set of $\minhits(Q/s)$, because otherwise at least
on $e\in [G(P)/s]^0$ would be accepted by $Q/s$. Now suppose that $\minhits(G(P)/s) = \varnothing$. Then   branch (\ref{eq:ufb}) can be entered, and the test 
stops after $\epass$. Otherwise, if $\minhits(G(P)/s) \neq \varnothing$, let
$H\in\minhits(G(P)/s)$. Since $H$ only contains elements that are contained in some minimal acceptance of $P/s$, and all these minimal acceptances are subsets of 
$[G(P)/s]^0$, $H$ is a subset of $[G(P)/s]^0$ as well. Since $[G(P)/s]^0$, however, 
is not an element of $\minhits(Q/s)$, also $H$ is not contained in $\minhits(Q/s)$.
Now this is a contradiction to Lemma~\ref{lemma:hseta}, since $Q\ conf\ P$ by assumption,
so $H$ should also be a (not necessarily minimal) hitting set in $\minhits(Q/s)$.
This proves that the test execution cannot block  at branch (\ref{eq:ufc})
without being able to pass the test by entering branch (\ref{eq:ufb}).

\paragraph{Step~2.2} Now suppose that the test execution blocks at 
branch (\ref{eq:ufd}) after having run through some $s\in\trc(Q)\subseteq \trc(P)$
with $\#s = j$.
From Lemma~\ref{lemma:ufproperties} we know
that $U_F(j)/s = U_F(j,k,n)$ with $U_F(j,k,n) = U_F(j,\#s,G(P)/s)$, so
$\minhits(n) = \minhits(P/s)$. The branch (\ref{eq:ufb}) of the test
$U_F(j,k,n)$ leads always to a PASS verdict and is taken if $\minhits(n) =
\varnothing$. 
If $\minhits(n) \neq \varnothing$,  the assumption that $(Q\parallel[\Sigma] U_F(j))/s$
blocks at branch (\ref{eq:ufd}) implies that there exists some $H\in\minhits(n)$
which is not a hitting set of $\minaccs(Q/s)$. Again, we can apply Lemma~\ref{lemma:hseta}
to conclude that this contradicts the assumption that $Q\ conf\ P$. As a consequence,
the test execution can never deadlock at branch (\ref{eq:ufd}) without entering
branch (\ref{eq:ufb}) and passing the test.

Note that the line of reasoning in this proof requires that $Q$ is free of
livelocks, because otherwise a $\epass$ event might not become visible,
due to unbounded sequences of hidden events performed by $Q$. 
\xbox
\end{proof}
%
\begin{lemma}\label{lemma:mainfexhaustive}
A test suite $\TS_F$ specified as in Theorem~\ref{th:failurestest} is
exhaustive for the fault model specified there.
\end{lemma}
\begin{proof}
Consider a process $Q\in{\cal D}$ with $P\not\lessdet_F Q$. According to
(\ref{eq:failconf}), this non-conformance can be caused in two possible ways
corresponding to the cases $P\not\lessdet_T Q$ and $\neg(Q\ conf\ P)$. These
cases can be characterised as follows:
\begin{description}
\item[Case~1] $\trc(Q)\not\subseteq \trc(P)$
\item[Case~2] There exists a joint trace $s\in\trc(Q)\cap\trc(P)$ and a minimal acceptance $A_Q$
of $\minaccs(Q/s)$, such that
(see Lemma~\ref{lemma:tgtrcref}, (\ref{eq:failrefb})).
\begin{equation}
\label{eq:accsnotcontained}
\forall A_P\in\minaccs(P/s): A_P\not\subseteq A_Q,
\end{equation}
\end{description}
It has to be shown for each of these cases that at least one test execution
of some $(Q\parallel[\Sigma] U_F(j))$ with $j < pq$ ends with the $\efail$
event or deadlocks. We do this by analysing the product graph of the
reference process $P$ and the SUT process $Q$: any trace
$s\in\trc(Q)\cap\trc(P)$ gives rise to a path labelled by the events of $s$
through this product graph. Any error can be detected after running through
such a trace and then either observing an event outside $[P/s]^0$ (this is
the violation described by Case~1) or identifying an illegal acceptance $A_Q$
as specified in Case~2. It is not guaranteed, however, that trace $s$ is
short enough to be executed by one of the test cases $U_F(j)$ with $0\le j <
pq$. So, it has to be shown that for any $s$ leading to an error situation
specified by Case~1 or Case~2, there exists a trace $u$ of maximal length
$pq-1$ leading to the same error.
